Smooth risk-based predictive approaches to treatment effect heterogeneity: A simulation study

### 2021-06-15 submission/manuscript.rmd
add proper figure captions

```{r rmsebase, echo=FALSE, fig.cap="RMSE base case", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_base.png"))
```

@@

```{r rmsesamplesize, echo=FALSE, fig.cap="Sample size 17000", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_sample_size.png"))
```

@@

```{r rmseauc, echo=FALSE, fig.cap="AUC 0.85", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_auc.png"))
```

@@

```{r discrimination, echo=FALSE, fig.cap="Discrimination for benefit base case.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/discrimination_base.png"))
```

@@

```{r calibration, echo=FALSE, fig.cap="Calibration for benefit base case.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/calibration_base.png"))
```

@@

```{r gusto, echo=FALSE, fig.cap="Caption", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/gusto.png"))
```

>>>>

```{r rmsebase, echo=FALSE, fig.cap="RMSE of the considered methods across 500 replications calculated in a simulated sample of size 500,000. \\textit{Panel A} presents the results under the base case scenario of true constant relative treatment effect, with a true prediction AUC of 0.75 and sample size of 4250; \\textit{Panel B} presents the results under moderate linear deviations from the base case of constant treatment effects, while holding true prediction AUC and sample size constant; \\textit{Panel C} presents the results for strong linear deviations from the base case scenario of constant relative treatment effects; \\textit{Panel D} presents the results for strong quadratic deviations from the base case scenario of constant relative treatment effects.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_base.png"))
```

@@

```{r rmsesamplesize, echo=FALSE, fig.cap="RMSE of the considered methods across 500 replications calculated in a simulated sample of size 500,000. \\textit{Panel A} presents the results under the base case scenario of true constant relative treatment effect, with a true prediction AUC of 0.75 and sample size of 17,000; \\textit{Panel B} presents the results under moderate linear deviations from the base case of constant treatment effects, while holding true prediction AUC and sample size constant; \\textit{Panel C} presents the results for strong linear deviations from the base case scenario of constant relative treatment effects; \\textit{Panel D} presents the results for strong quadratic deviations from the base case scenario of constant relative treatment effects.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_sample_size.png"))
```

@@

```{r rmseauc, echo=FALSE, fig.cap="RMSE of the considered methods across 500 replications calculated in a simulated sample of size 500,000. \\textit{Panel A} presents the results under the base case scenario of true constant relative treatment effect, with a true prediction AUC of 0.85 and sample size of 4,250; \\textit{Panel B} presents the results under moderate linear deviations from the base case of constant treatment effects, while holding true prediction AUC and sample size constant; \\textit{Panel C} presents the results for strong linear deviations from the base case scenario of constant relative treatment effects; \\textit{Panel D} presents the results for strong quadratic deviations from the base case scenario of constant relative treatment effects.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_auc.png"))
```

@@

```{r discrimination, echo=FALSE, fig.cap="Discrimination for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. \\textit{Panel A} presents the results under the base case scenario of true constant relative treatment effect, with a true prediction AUC of 0.75 and sample size of 4250; \\textit{Panel B} presents the results under moderate linear deviations from the base case of constant treatment effects, while holding true prediction AUC and sample size constant; \\textit{Panel C} presents the results for strong linear deviations from the base case scenario of constant relative treatment effects; \\textit{Panel D} presents the results for strong quadratic deviations from the base case scenario of constant relative treatment effects.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/discrimination_base.png"))
```

@@

```{r calibration, echo=FALSE, fig.cap="Calibration for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. \\textit{Panel A} presents the results under the base case scenario of true constant relative treatment effect, with a true prediction AUC of 0.75 and sample size of 4250; \\textit{Panel B} presents the results under moderate linear deviations from the base case of constant treatment effects, while holding true prediction AUC and sample size constant; \\textit{Panel C} presents the results for strong linear deviations from the base case scenario of constant relative treatment effects; \\textit{Panel D} presents the results for strong quadratic deviations from the base case scenario of constant relative treatment effects.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/calibration_base.png"))
```

@@

```{r gusto, echo=FALSE, fig.cap="Individualized absolute benefit predictions based on baseline risk when using a constantn treatment effect approach, a linear interaction approach and RCS smoothing using 3,4 and 5 knots. Risk stratified estimates of absolute benefit are presented within quartiles of baseline risk as reference.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/gusto.png"))
```

# Discussion
